---
title: 'EDS 241: Assignment 2'
author: "Alexandra Yousefivand"
date: '`r format(Sys.time(), "%m/%d/%Y")`'
output: 
  pdf_document:
    toc: false
    number_sections: yes
header-includes:
  \setlength{\parindent}{1em}
  \usepackage{float}
  \renewcommand{\thesection}{Question (\alph{section})}
---

``` {r setup, echo = FALSE, message = FALSE, warning = FALSE}

# set default chunk options
knitr::opts_chunk$set(fig.width = 4, fig.height = 3,
                      echo = TRUE, message = FALSE, warning = FALSE)                     
```


```{r}
# load packages
packages=c("stargazer", "here", "tidyr", "dplyr","stringr", "janitor", 
           "cowplot", "ggplot2", "tinytex", "datasets", "tibble", "estimatr")

for (i in packages) {
  if (require(i,character.only=TRUE)==FALSE) {
    install.packages(i,repos='http://cran.us.r-project.org')
  }
  else {
    require(i,character.only=TRUE)
  }
}

#devtools::install_github('rstudio/rmarkdown')
options(scipen=999) # not scientific notation
```

```{r}
# load data
data_raw <- read.csv("NBP.csv")

data <- data_raw %>% clean_names()
```


# Histogram

```{r}
histogram <- ggplot(data = data, mapping = aes(x = dnox_masstons)) +
                    geom_histogram() +
                    labs(x = "Change in NOX (mass tons)")

histogram
```

# Indicator = 1 if pct_black > sample median, 0 otherwise

```{r}
# create indicator variable column
data <- mutate(.data = data,
                  D = case_when(pct_black >  median(data$pct_black) ~ 1,
                                pct_black <= median(data$pct_black) ~ 0))
```

```{r}
data_1 <- filter(.data = data, D == 1)

avg_pct_black <- mean(data_1$pct_black)
print(paste0(round(avg_pct_black, 2), "%"))
```

# Regression

```{r}
model <- lm_robust(formula = dnox_masstons ~ nbp, data = data)
summary(model)
```

**Intercept** =  `r round(model$coefficient[1], 3)` tons

\noindent If the county was NOT regulated under the NOx Budget Program (NBP = 0), the change in annual NOx emissions from all power plants in that county between 2000 and 2008

**Slope coefficient** = `r round(model$coefficient[2], 3)` tons

\noindent The difference in the change in annual NOx emissions from all power plants between 2000 and 2008 in a county regulated under the NOx Budget Program and another county NOT regulated under the NOx Budget Program (i.e. regulation / no regulation difference in annual NOx emissions)

# Interaction between NBP andd D

```{r}
model_interaction <- lm_robust(formula = dnox_masstons ~ nbp + D + nbp:D,
                               data = data)
summary(model_interaction)
```

??????????

**Intercept**: `r round(model$coefficient[1], 3)` tons

\noindent The change in annual NOx emissions from all power plants in a county between 2000 and 2008, if the county was NOT regulated under the NOx Budget Program (NBP = 0)

**NBP coefficient** = `r round(model_interaction$coefficient[2], 3)` tons

\noindent The difference in the change in annual NOx emissions from all power plants between 2000 and 2008 in a county regulated under the NOx Budget Program and another county NOT regulated under the NOx Budget Program (i.e. regulation / no regulation difference in annual NOx emissions)

**D coefficient** = `r round(model_interaction$coefficient[3], 3)` tons

\noindent The difference in the change in annual NOx emissions from all power plants between 2000 and 2008 in a county with pct_black above the sample median compared to a county with pct_black below the sample median.


**Interaction coefficient** = `r round(model_interaction$coefficient[4], 3)` tons

\noindent The difference in the change in annual NOx emissions from all power plants between 2000 and 2008 in a county regulated under the NOx Budget Program and with pct_black above the sample median compared to another county NOT regulated under the NOx Budget Program and below the sample median.


??????????


# Prediction and 95% confidence interval